Transfer report

### 2018-06-14 Report/progress-report.Rmd
Updates scripts to the almost final poreprocessing stage

sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
#load("../multi.data")
load("../settings.data")
df_participants <- settings$participants
df_participants$condition <- paste0(df_participants$First.phase, "-", df_participants$Second.phase)
```

>>>>

sop_all <- read.table("../sop_smoothed.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk_smoothed.csv", sep=";", header = T, stringsAsFactors = F)
#load("../multi.data")
load("../settings.data")
df_participants <- settings$participants
df_participants$condition <- paste0(df_participants$First.phase, "-", df_participants$Second.phase)
```

### 2018-06-14 Report/smoothness-report.Rmd
Updates scripts to the almost final poreprocessing stage

sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_smoothed <- read.table("../walk_smoothed.csv", sep=";", header = T, stringsAsFactors = F)
```

>>>>

sop_all <- read.table("../sop_smoothed.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
walk_smoothed <- read.table("../walk_smoothed.csv", sep=";", header = T, stringsAsFactors = F)
```

### 2018-06-14 Report/transfer-report.Rmd
Updates scripts to the almost final poreprocessing stage

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
library(broom)

@@

# Block measures

```{r, echo = F}
condition_all_sums <- conference_walk_all %>% 
  group_by(exp_block_id, id, condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = mean((block3-block4)/(block4+block3), na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = mean((block1-block4)/(block1+block4), na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```
Block 43 diff is now flipped to (block4 - block3)/(block4 + block3) and block41 is the forth and first.

There were several ways how I could calculate it. Eventually, the block 4 data are sums of errors per person and block and average path is the average normalised path for a block per person.

Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")

@@

@@

## Anova
This is simple mixed anova (for those three conditions) I know how to do in R. Not sure how to do contrasts and within add subject error variability, nor how to run post hocs. I expect Mike will be able to do that in his models for the paper.

```{r}
aov_block_distance <- aov(min_norm_distance~exp_block_id*condition, conference_walk_all)
summary(aov_block_distance)
```

@@

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(ez)
library(dplyr)
library(reshape2)
library(broom)

@@

# Block measures
```{r, echo = F}
condition_all_sums <- conference_walk_all %>% 
  group_by(exp_block_id, id, condition) %>% 
  summarise(sum.distance = sum(min_norm_distance, na.rm = T), 
            sum.errors = sum(errors, na.rm = T),
            mean.distance = mean(min_norm_distance, na.rm = T),
            mean.error = mean(errors, na.rm = T))

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = mean((block3-block4)/(block4+block3), na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = mean((block1-block4)/(block1+block4), na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```

## Sum of errors

Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + ylab("Mean sum of errors")

@@

## Normalised distance

@@

@@

## Anova
Simple between subjects anova
```{r}
aov_block_distance <- aov(min_norm_distance~exp_block_id*condition, conference_walk_all)
summary(aov_block_distance)
```

```{r}
ez_prepare_block <- function(df, blocks){
  filtered_data <- df[df$exp_block_id %in% blocks, ]
  filtered_data <- filtered_data[complete.cases(filtered_data),]
  has_all <- filtered_data %>% group_by(id) %>% select(id, "exp_block_id") %>% unique() %>% count
  has_all <- has_all %>% filter(n == 2)
  filtered_data <- filtered_data %>% filter(id %in% has_all$id)
  filtered_data$exp_block_id <- factor(filtered_data$exp_block_id)
  return(filtered_data)
}

clean_walk_14 <- ez_prepare_block(conference_walk_all, c(1,4))
clean_walk_34 <- ez_prepare_block(conference_walk_all, c(3,4))
```

### Normalised distance

Within subjects anova for block 3-4 difference.

```{r, warning = F, echo=F, message=F}
aov_block_dist_34 <- ezANOVA(
  data = clean_walk_34,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = condition, 
  type = 3)
aov_block_dist_34

ggplot(clean_walk_34, aes(x = as.numeric(exp_block_id), y = min_norm_distance, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average normalised distance") + xlab("Experimental block") + scale_fill_discrete("Condition")
```

Within subjects anova for block 1-4 difference in minimal path.

```{r, warning = F, echo=F, message=F}

aov_block_dist_14 <- ezANOVA(
  data = clean_walk_14,
  dv = min_norm_distance, 
  wid = id,
  within = exp_block_id,
  between = condition,
  type = 3)
aov_block_dist_14

ggplot(clean_walk_14, aes(x = as.numeric(exp_block_id), y = min_norm_distance, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average normalised distance") + xlab("Experimental block") + scale_fill_discrete("Condition")
```

### NUmber of errors
Within subjects anova for block 1-4 number of errors.

```{r, warning = F, echo=F, message=F}
aov_block_err_14 <- ezANOVA(
  data = clean_walk_14,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = condition,
  type = 3)
aov_block_err_14

ggplot(clean_walk_14, aes(x = as.numeric(exp_block_id), y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average number of errors") + xlab("Experimental block") + scale_fill_discrete("Condition")
```

Within subjects anova for block 3-4 number of errors.
```{r, warning = F, echo=F, message=F}
aov_block_err_34 <- ezANOVA(
  data = clean_walk_34,
  dv = errors, 
  wid = id,
  within = exp_block_id,
  between = condition,
  type = 3)
aov_block_err_34

ggplot(clean_walk_34, aes(x = as.numeric(exp_block_id), y = errors, color = factor(condition))) +
  stat_summary(fun.data=mean_cl_normal,position=position_dodge(width=0.1), width = 0.2, geom="errorbar") + 
  stat_summary(fun.y=mean,position=position_identity(), size = 1, geom="line") + 
  ylab("Average number of errors") + xlab("Experimental block") + scale_fill_discrete("Condition")
```
